---
title: "WordRec Experiment"
author: "A. Fourtassi"
date: "November 26, 2018"
output:
  html_document:
    number_sections: yes
    toc: yes
---
Libraries.

```{r}
library(papaja)
library(kableExtra)
library(readr)
library(purrr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(knitr)
library(nlstools)
library(boot)
library(dplyr)
library(langcog)
library(ggthemes)
library(broom)
```

Data and processing
```{r}

#Data from the 3 experiments 
#############################
exp1 <- read_delim("data_exp1_anonym.txt", delim = " ") %>%
  filter(type == "Task") %>%
  mutate(experiment='Experiment1')

exp2 <- read_delim("data_exp2_anonym.txt", delim = " ") %>%
  filter(type == "Task") %>%
  mutate(experiment='Experiment2')

exp3 <- read_delim("data_exp3_anonym.txt", delim = " ") %>%
  filter(type == "Task") %>%
  mutate(experiment='Experiment3')

exp4 <- read_delim("data_rev_real1.txt", delim = " ") %>%
  filter(type == "Task") %>%
  mutate(experiment='Experiment4')


```


```{r}
#First Exlusion criteria:
#############################

#All data

N_all_1 <- exp1 %>%
  distinct(ID) %>%
  nrow()

N_all_2 <- exp2 %>%
  distinct(ID) %>%
  nrow()

N_all_3 <- exp3 %>%
  distinct(ID) %>%
  nrow()

N_all_4 <- exp4 %>%
  distinct(ID) %>%
  nrow()

#Participants who did not encounter a technical problem with the online experiment
 
#Exp1
exp1_noProb <- exp1 %>%
  filter(problem=="No") 

N_noProb_1 <- exp1_noProb %>%
  distinct(ID) %>%
  nrow()


#Exp2
exp2_noProb <- exp2 %>%
  filter(problem=="No") 

N_noProb_2 <- exp2_noProb %>%
  distinct(ID) %>%
  nrow()

#Exp3
exp3_noProb <- exp3 %>%
  filter(problem=="No") 

N_noProb_3 <- exp3_noProb %>%
  distinct(ID) %>%
  nrow()

#Exp 4
exp4_noProb <- exp4 %>%
  filter(problem=="No") 

N_noProb_4 <- exp4_noProb %>%
  distinct(ID) %>%
  nrow()

#Participants who who did not encounter a problem AND were above 50% accuracy on obvious trials

#Exp1
exp1_good <- exp1_noProb %>%
  filter(score > 0.5)

N_good_1 <- exp1_good %>%
  distinct(ID) %>%
  nrow()

#Exp2
exp2_good <- exp2_noProb %>%
  filter(score > 0.5)

N_good_2 <- exp2_good %>%
  distinct(ID) %>%
  nrow()

#Exp3
exp3_good <- exp3_noProb %>%
  filter(score > 0.5)

N_good_3 <- exp3_good %>%
  distinct(ID) %>%
  nrow()

#Exp 4 (The change in the selection threshold in 1 bis was re-registered: the longer experiment required stricter quality control)
exp4_good <- exp4_noProb %>%
  filter(score >= 0.75)

N_good_4 <- exp4_good %>%
  distinct(ID) %>%
  nrow()
```



```{r}
#Data subseting

#Experiment 1
##############

exp_good <- bind_rows(exp1_good, exp2_good, exp3_good, exp4_good)
  

sounds_exp <- exp_good %>%
  filter(condition == "sound") %>%
  group_by(experiment, sound_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Condition="Auditory") %>%
  rename(distance = sound_dist)

concepts_exp <- exp_good %>%
  filter(condition == "concept") %>%
  group_by(experiment, concept_dist) %>%
  dplyr::summarise(mean = mean(answer),
                   sd = sd(answer),
                   n = n()) %>%
  mutate(se = sd / sqrt(n),
         lower = mean - qt(1 - (0.05 / 2), n - 1) * se,
         upper = mean + qt(1 - (0.05 / 2), n - 1) * se) %>%
  select(-sd, -n, -se,) %>%
  mutate(Condition="Visual") %>%
  rename(distance = concept_dist)

joint_exp <- exp_good %>%
  filter(condition == "joint") %>%
  group_by(experiment, concept_dist, sound_dist) %>%
  summarise(mean = mean(answer)) %>%
  mutate(Condition="joint") 

#Combine all
exp_uni <- bind_rows(sounds_exp, concepts_exp)

#feather::write_feather(exp_uni, "saved_data/exp_uni.feather")
exp_uni <- feather::read_feather("saved_data/exp_uni.feather")
```



```{r}

#Fit models to the reponses

fit_s <- function(data){
  nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=data, start = list(e=0, vrA=2))
}

fit_c <- function(data){
  nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=data, start = list(e=0, vrV=2))
}

fit_j <- function(data){
  nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=data, start = list(e=0, vrA_j=2, vrV_j=2))
}

exp_good_s <- exp_good %>% filter(condition =='sound')
exp_good_c <- exp_good %>% filter(condition =='concept')
exp_good_j <- exp_good %>% filter(condition =='joint')

data_by_exp_s <- split(exp_good_s, exp_good_s$experiment) 
data_by_exp_c <- split(exp_good_c, exp_good_c$experiment)
data_by_exp_j <- split(exp_good_j, exp_good_j$experiment)

model_by_exp_s <- map(data_by_exp_s, fit_s) 
model_by_exp_c <- map(data_by_exp_c, fit_c)
model_by_exp_j <- map(data_by_exp_j, fit_j)


```

Extract coefficients
```{r}
##Extract coefficients 
####################

#Unimodal coefficients
 co_s <- function(model, exp) {
   data.frame(bias_s=coefficients(model)[1],
              bias_s_low = confint2(model)[1,][1],
              bia_s_up = confint2(model)[1,][2],
              
              var_s=coefficients(model)[2], 
              var_s_low = confint2(model)[2,][1],
              var_s_up = confint2(model)[2,][2],
              
              experiment=exp)
 }
 
  co_c <- function(model, exp) {
   data.frame(bias_c=coefficients(model)[1],
              bias_c_low = confint2(model)[1,][1],
              bias_c_up = confint2(model)[1,][2],
              
              var_c= coefficients(model)[2], 
              var_c_low = confint2(model)[2,][1],
              var_c_up = confint2(model)[2,][2],
              
              experiment=exp)
 }
 
 #Bimodal coefficients
 co_j <- function(model, exp) {
   data.frame(bias_j=coefficients(model)[1],
              bias_j_low = confint2(model)[1,][1],
              bias_j_up = confint2(model)[1,][2],
              
              var_j_s=coefficients(model)[2],
              var_j_s_low = confint2(model)[2,][1],
              var_j_s_up = confint2(model)[2,][2],
              
              var_j_c=coefficients(model)[3],
              var_j_c_low = confint2(model)[3,][1],
              var_j_c_up = confint2(model)[3,][2],
              
              experiment=exp)
 }

 experiment <- as.list(strsplit(names(model_by_exp_s), " "))
 
coef_s <- map2(model_by_exp_s, experiment, co_s) %>%
  bind_rows() 
 
coef_c <- map2(model_by_exp_c, experiment, co_c) %>%
  bind_rows() 

coef_j <- map2(model_by_exp_j, experiment, co_j) %>%
  bind_rows() 

parameters <- coef_s %>%
  right_join(coef_c) %>%
  right_join(coef_j) %>%
  select(experiment, bias_s, var_s, bias_c, var_c, bias_j, var_j_s, var_j_c) %>%
  mutate(bias_s = - bias_s,
         bias_c = - bias_c, 
         bias_j = - bias_j)

#feather::write_feather(parameters, "saved_data/parameters.feather")
parameters <- feather::read_feather("saved_data/parameters.feather")


```

Parameter values (! change kable format to "pdf")

```{r stats, results="asis", echo=FALSE}

kable(parameters, escape = FALSE, booktabs = TRUE,
      linesep = "", format.args = list(big.mark = ","),
      caption = "Statistics for the dataset we used."#,
      #col.names = c("Language",  "Nouns", "Ages", "N", "Nouns", "Ages","N")
      ) %>%
  add_header_above(c("", "Auditory" = 2, "Visual" = 2, "Bimodal" = 3 )) %>%
  column_spec(1, bold = TRUE) %>%
  kable_styling(position = "center")

```

Unuimodal condition
```{r}
##Generate predictions  
######################

x <- seq(0, 4, 0.01)

pr_s <- function(model, exp){
  y <- predict(model, list(sound_dist = x), type="response")
  data.frame(distance=x, prediction=y, experiment=exp, Condition = "Auditory") 
}

pr_c <- function(model, exp){
  y <- predict(model, list(concept_dist = x), type="response")
  data.frame(distance=x, prediction=y, experiment=exp, Condition = "Visual") 
}

pred_s <- map2(model_by_exp_s, experiment, pr_s) %>%
  bind_rows() 

pred_c <- map2(model_by_exp_c, experiment, pr_c) %>%
  bind_rows() 

pred_uni <- bind_rows(pred_s, pred_c) 

#feather::write_feather(pred_uni, "saved_data/pred_uni.feather")
pred_uni <- feather::read_feather("saved_data/pred_uni.feather")

### plot all
ggplot(exp_uni, 
       aes(x = distance, y = mean)) + 
  #geom_point()+
  geom_pointrange(aes(ymin = lower, ymax = upper), 
                  position = position_dodge(width = .1), size = 0.4, fatten = 2) + 
  #geom_line(data=uniV,aes(x=xV, y=yV))+
  geom_line(data=pred_uni, aes(x=distance, y=prediction), col='black')+
  xlab("Distance") +ylab("Prob. different")+
  scale_y_continuous(limits = c(0, 1))+#theme(aspect.ratio = 0.7)+
  theme_few()+
  theme(aspect.ratio = 0.7) + facet_grid(experiment ~ Condition)
  #stat_function(fun = Logistic_v, colour="red"))


```

Bimodal condition: iptimality analysis
```{r}

#First define all models 

# Sound only
model_s <- function (data, x,y) {
  vrA = unique(data$var_s)
  b = unique(data$bias_s)
  
  1/(1 + (1-b)*exp((-4/vrA)*x+(8/vrA)))
}

# Visual only
model_c <- function (data, x,y) {
  vrV = unique(data$var_c)
  b = unique(data$bias_c)
  
  1/(1 + (1-b)*exp((-4/vrV)*y+(8/vrV)))
}

# Optimal
model_opt <- function (data, x,y) {
  vrA = unique(data$var_s)
  vrV = unique(data$var_c)
  e   = unique(data$bias_j)
  
  1/(1 + (1-e)*exp((-4/vrA)*x+(-4/vrV)*y+(8/vrA)+(8/vrV)))
}

# Descriptive
model_des <- function (data, x,y) {
  vrA = unique(data$var_j_s)
  vrV = unique(data$var_j_c)
  e   = unique(data$bias_j)
  
  1/(1 + (1-e)*exp((-4/vrA)*x+(-4/vrV)*y+(8/vrA)+(8/vrV)))
}

data_and_models <- joint_exp %>%
  left_join(coef_s) %>%
  left_join(coef_c) %>%
  left_join(coef_j)

models <- function (data) {
  data %>% rename(Joint = mean) %>%
  mutate(Descriptive = model_des(data, sound_dist, concept_dist)) %>%
  mutate(Optimal = model_opt(data, sound_dist, concept_dist)) %>%
  mutate(Auditory = model_s(data, sound_dist, concept_dist)) %>%
  mutate(Visual = model_c(data, sound_dist, concept_dist)) %>%
  gather(model, pred, Visual, Auditory, Optimal, Descriptive) 
}

data_by_exp <- split(data_and_models, data_and_models$experiment) 

pred_bimod <- map(data_by_exp, models) %>%
  bind_rows()


#Caclculate correlation
modelCorr <- pred_bimod %>%
  group_by(experiment, model) %>%
  summarise(cor = round(cor(Joint, pred)^2, 2))

pred_bimod <- pred_bimod %>%
  left_join(modelCorr)

#feather::write_feather(pred_bimod, "saved_data/all_bimod.feather")
pred_bimod <- feather::read_feather("saved_data/all_bimod.feather")
```

main plot 
```{r}
pred_bimod$model <- factor(pred_bimod$model, levels = c('Visual','Auditory', 'Optimal', 'Descriptive'))

ggplot(pred_bimod, 
       aes(x = pred, y = Joint, col = factor(concept_dist), 
           shape = factor(sound_dist))) + 
  geom_point(size =1)+
  scale_colour_solarized()+
 #geom_pointrange(aes(ymin = summary_ci_lower, ymax = summary_ci_upper), 
  #                position = position_dodge(width = .1), size=0.2) + 

  geom_abline(slope = 1, lty = 2) +
  #annotate("text",aes(label=paste("R^2 ==", cor, sep="")), x=0.1, y=0.9, size=2, col='black', fontface = "bold", parse=TRUE)+
  geom_text(aes(label=paste("r^2 ==", cor, sep="")), x=0.15, y=0.9, size=2, col='black',fontface = "bold", parse=TRUE)+
  xlab("Predictions") +ylab("Human data")+
  facet_grid(experiment ~ model)+
  theme_few()+
theme(aspect.ratio = 0.7, 
      axis.text=element_text(size=6),
      strip.text.y = element_text(size = 8))+
  guides(color=guide_legend(title="Visual Distance")) +
  guides(shape=guide_legend(title="Auditory Distance")) 
```

Bootsrap resampling of the cue combination weights 


```{r echo=FALSE}

#Bootstrap sample of parameters

lmfit <- function(data, indices) {
  
  myd = data[indices, ]
  
  s_data <- myd %>%
    filter(condition == "sound")

  v_data <- myd %>%
    filter(condition == "concept") 

  j_data <- myd %>%
    filter(condition == "joint")
    
  s_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), data=s_data, start = list(e=0, vrA=2), nls.control(warnOnly = TRUE))

 c_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), data=v_data, start = list(e=0, vrV=2), nls.control(warnOnly = TRUE))

 j_nl <- nls(answer ~ 1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), data=j_data, start = list(e=0, vrA_j=2, vrV_j=2), nls.control(warnOnly = TRUE))

  
  s_va <- coefficients(s_nl)["vrA"]
  s_e <- coefficients(s_nl)["e"]
  
  v_va <- coefficients(c_nl)["vrV"]
  v_e <- coefficients(c_nl)["e"]
  
  decision_ideal=v_va/s_va

  j_va_s=coefficients(j_nl)["vrA_j"]
  j_va_v=coefficients(j_nl)["vrV_j"]
  j_e=coefficients(j_nl)["e"]
  
  decision_fit=j_va_v/j_va_s
  
  preference = decision_fit/decision_ideal
  
  MyBoot=c(s_va, s_e, v_va, v_e, j_va_s, j_va_v, j_e, decision_ideal, decision_fit, preference)
  
  
  return(MyBoot) 

  }

```

experiment 1 (too long, need to re-write this)
```{r echo=FALSE}
#results1 <- boot(data=exp1_good, statistic = lmfit, R = 10000)

#dataSave1 <- data.frame(matrix(ncol = 5, nrow = 0))
#data_names <- c("variable", "estimate", "lower","upper", "Experiment")
#colnames(dataSave1) <- data_names

#Auditory variance:
#audVar=boot.ci(results1, index = 1, type = c("bca"), conf = 0.95)

#v1 <- data.frame('audVar', as.numeric(audVar$t0), as.numeric(audVar$bca[4]), as.numeric(audVar$bca[5]), 'Exp1')
#  colnames(v1) <- data_names

#Auditory bias:
#audBias=boot.ci(results1, index = 2, type = c("bca"), conf = 0.95)

#v2 <- data.frame('audBias', as.numeric(audBias$t0), as.numeric(audBias$bca[4]), as.numeric(audBias$bca[5]), 'Exp1')
#colnames(v2) <- data_names

#Visual variance:
#visVar=boot.ci(results1, index = 3, type = c("bca"), conf = 0.95)

#v3 <- data.frame('visVar', as.numeric(visVar$t0), as.numeric(visVar$bca[4]), as.numeric(visVar$bca[5]), 'Exp1')
#colnames(v3) <- data_names


#Visual bias:
#visBias=boot.ci(results1, index = 4, type = c("bca"), conf = 0.95)

#v4 <- data.frame('visBias', as.numeric(visBias$t0), as.numeric(visBias$bca[4]), as.numeric(visBias$bca[5]), 'Exp1')
#colnames(v4) <- data_names


#Bimodal Auditory variance:
#audVarBi=boot.ci(results1, index = 5, type = c("bca"), conf = 0.95)

#v5 <- data.frame('audVarBi', as.numeric(audVarBi$t0), as.numeric(audVarBi$bca[4]), as.numeric(audVarBi$bca[5]), 'Exp1')
#colnames(v5) <- data_names


#Bimodal Visual variance:
#visVarBi=boot.ci(results1, index = 6, type = c("bca"), conf = 0.95)

#v6 <- data.frame('visVarBi', as.numeric(visVarBi$t0), as.numeric(visVarBi$bca[4]), as.numeric(visVarBi$bca[5]), 'Exp1')
#colnames(v6) <- data_names

#Bimodal bias:
#BiasBi=boot.ci(results1, index = 7, type = c("bca"), conf = 0.95)

#v7 <- data.frame('BiasBi', as.numeric(BiasBi$t0), as.numeric(BiasBi$bca[4]), as.numeric(BiasBi$bca[5]), 'Exp1')
#colnames(v7) <- data_names

#Ideal modality wieghing
#prefIdeal=boot.ci(results1, index = 8, type = c("bca"), conf = 0.95)

#v8 <- data.frame('prefIdeal', as.numeric(prefIdeal$t0), as.numeric(prefIdeal$bca[4]), as.numeric(prefIdeal$bca[5]), 'Exp1')
#colnames(v8) <- data_names


#fit modality wieghing
#prefFit=boot.ci(results1, index = 9, type = c("bca"), conf = 0.95)

#v9 <- data.frame('prefFit', as.numeric(prefFit$t0), as.numeric(prefFit$bca[4]), as.numeric(prefFit$bca[5]), 'Exp1')
#colnames(v9) <- data_names


#Modality bias 
#bias=boot.ci(results1, index = 10, type = c("bca"), conf = 0.95)

#v10 <- data.frame('bias', as.numeric(bias$t0), as.numeric(bias$bca[4]), as.numeric(bias$bca[5]), 'Exp1')
#colnames(v10) <- data_names



#dataSave1 <- bind_rows(dataSave1, v1, v2, v3, v4, v5, v6, v7, v8, v9, v10)

#feather::write_feather(dataSave1, "dataExp1.feather")

dataSave1 <- feather::read_feather("dataExp1.feather")

###### Extract values from saved data 
##To reproduce the values, please uncomment the previous code following the function "lmfit"

prefIdeal_val_1=dataSave1$estimate[which(dataSave1$variable == "prefIdeal")]
prefIdeal_ci1_1=dataSave1$lower[which(dataSave1$variable == "prefIdeal")]
prefIdeal_ci2_1=dataSave1$upper[which(dataSave1$variable == "prefIdeal")]

prefFit_val_1=dataSave1$estimate[which(dataSave1$variable == "prefFit")]
prefFit_ci1_1=dataSave1$lower[which(dataSave1$variable == "prefFit")]
prefFit_ci2_1=dataSave1$upper[which(dataSave1$variable == "prefFit")]

bias_val_1=dataSave1$estimate[which(dataSave1$variable == "bias")]
bias_ci1_1=dataSave1$lower[which(dataSave1$variable == "bias")]
bias_ci2_1=dataSave1$upper[which(dataSave1$variable == "bias")]

#With exactly the same procedure, we get the paramters for experiment 2 and 3 (experiment 4 has its own, separate analysis)
dataSave2 <- feather::read_feather("dataExp2.feather")
dataSave3 <- feather::read_feather("dataExp3.feather")


#Exp2
prefIdeal_val_2=dataSave2$estimate[which(dataSave2$variable == "prefIdeal")]
prefIdeal_ci1_2=dataSave2$lower[which(dataSave2$variable == "prefIdeal")]
prefIdeal_ci2_2=dataSave2$upper[which(dataSave2$variable == "prefIdeal")]

prefFit_val_2=dataSave2$estimate[which(dataSave2$variable == "prefFit")]
prefFit_ci1_2=dataSave2$lower[which(dataSave2$variable == "prefFit")]
prefFit_ci2_2=dataSave2$upper[which(dataSave2$variable == "prefFit")]

bias_val_2=dataSave2$estimate[which(dataSave2$variable == "bias")]
bias_ci1_2=dataSave2$lower[which(dataSave2$variable == "bias")]
bias_ci2_2=dataSave2$upper[which(dataSave2$variable == "bias")]

#Exp3
prefIdeal_val_3=dataSave3$estimate[which(dataSave3$variable == "prefIdeal")]
prefIdeal_ci1_3=dataSave3$lower[which(dataSave3$variable == "prefIdeal")]
prefIdeal_ci2_3=dataSave3$upper[which(dataSave3$variable == "prefIdeal")]

prefFit_val_3=dataSave3$estimate[which(dataSave3$variable == "prefFit")]
prefFit_ci1_3=dataSave3$lower[which(dataSave3$variable == "prefFit")]
prefFit_ci2_3=dataSave3$upper[which(dataSave3$variable == "prefFit")]

bias_val_3=dataSave3$estimate[which(dataSave3$variable == "bias")]
bias_ci1_3=dataSave3$lower[which(dataSave3$variable == "bias")]
bias_ci2_3=dataSave3$upper[which(dataSave3$variable == "bias")]


```

Modality preference

```{r echo=FALSE, warning = FALSE}

#Modality preference in an audio-vidual space

# Decision threshold
classif = function (x, A) {
    2*A+2-A*x
}

pref_data <- data.frame(matrix(ncol = 7, nrow = 0))
names <- c("Auditory", "Visual", "Optimal", "Auditory bias", "Visual bias", "Fit", "Experiment")
colnames(pref_data) <- names

x=seq(-1,5,0.02)

pref_exp1 <- data.frame(x, x, 
                        classif(x, prefIdeal_val_1),
                        classif(x, 2*prefIdeal_val_1),
                        classif(x, 0.5*prefIdeal_val_1),
                        classif(x, prefFit_val_1),
                        'Exp1')
colnames(pref_exp1) <- names

pref_exp2 <- data.frame(x, x, 
                        classif(x, prefIdeal_val_2),
                        classif(x, 2*prefIdeal_val_2),
                        classif(x, 0.5*prefIdeal_val_2),
                        classif(x, prefFit_val_2),
                        'Exp2')
colnames(pref_exp2) <- names

pref_exp3 <- data.frame(x, x, 
                        classif(x, prefIdeal_val_3),
                        classif(x, 2*prefIdeal_val_3),
                        classif(x, 0.5*prefIdeal_val_3),
                        classif(x, prefFit_val_3),
                        'Exp3')
colnames(pref_exp3) <- names

pref_data <- bind_rows(pref_data, pref_exp1, pref_exp2, pref_exp3) %>%
  gather(model, value, Optimal:Fit)

pref_data$model <- factor(pref_data$model, levels = c("Optimal", "Fit","Auditory bias", "Visual bias"))

feather::write_feather(pref_data, "pref_data.feather")
pref_data <- feather::read_feather("pref_data.feather")
  
pref_thres <- ggplot(pref_data, aes(x=Auditory, y=value, col = factor(model))) +
  geom_line(aes(linetype = factor(model) )) +
  facet_grid(.~Experiment)+
  scale_colour_manual(values = c("Optimal" = "red", "Auditory bias" = "blue", "Visual bias" = "green", "Fit" = "black"))+
  scale_linetype_manual(values = c("Optimal" = "solid", "Auditory bias" = "dashed", "Visual bias" = "dashed", "Fit" = "solid"))+
  xlab("Auditory") +ylab("Visual") +
  scale_x_continuous(limits = c(1.7, 2.3))+
  scale_y_continuous(limits = c(1.7, 2.3))+
  theme_few()+
  theme(aspect.ratio = 1)+
  theme(legend.title = element_blank())

```


```{r echo=FALSE, warning = FALSE}


#Modality bias
preference = c(bias_val_1, bias_val_2, bias_val_3)
experiment =c("Exp 1 \n", "Exp 2", "Exp 3")
ci_low=c(bias_ci1_1, bias_ci1_2, bias_ci1_3)
ci_up=c(bias_ci2_1, bias_ci2_2, bias_ci2_3)

pref = data.frame(preference, ci_low, ci_up)

bias <- ggplot(pref, 
       aes(x = experiment, y=preference)) +
  geom_hline(yintercept = 1, linetype='solid', color="red", size=1)+
  geom_hline(yintercept = 0.5, linetype=2, color="green")+
  geom_hline(yintercept = 2, linetype=2, color="blue")+
  geom_point(size=3)+
  geom_errorbar(aes(ymin = ci_low, ymax = ci_up), 
                  width = 0.1,
                  position = position_dodge(width = 0.1))+
  theme_few()+
  theme(aspect.ratio = 1, axis.text=element_text(size=10))+
  xlab("") +ylab("Relative weighting")+
  scale_y_log10(breaks=c(0.5,1,2),labels=c("Visual bias","Optimal","Auditory bias"))
  
  #coord_cartesian(ylim=c(0, 2.5))

```

```{r bias, echo=FALSE, warning = FALSE, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Modality preference is characterized as a deviation from the optimal decision threshold. A) The decision thresholds of both the optimal and the descriptive models (solid red and black lines, respectively). Deviation from optimality is compared to two hypothetical cases of modality preference. In these cases, deviation from  optimality is due to over-lying on the visual or the auditory input by a factor of 2 (green and blue dotted lines, respectively). B) An alternative way to represent the same data. Each point represents the value of the decision threshold's slope derived from the descriptive model relative to that of the optimal model (log-scaled). The lines represent the optimal case as well as the two hypothetical cases of modality preference. Error bars represent 95\\% confidence intervals over the distribution obtained through non-parametric resampling."}

legend <- get_legend(pref_thres)
plot_noLegend <- plot_grid(pref_thres + theme(legend.position="none"), NULL, bias, labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.1, 0.1, 1.3))
plot_grid(plot_noLegend, legend, rel_widths = c(2, .5))

```

Individual analysis (Experiment 4)

First simulate answers based on the population level probabilistic model (we will analyse both real and simualted answers simultaneousely)
```{r}
#First define all models, 

param <- parameters %>%
  filter(experiment =="Experiment4")

vrA = param$var_s
  bA = param$bias_s
  
vrV = param$var_c
  bV = param$bias_c
  
vrAj = param$var_j_s
vrVj = param$var_j_c
  bj = param$bias_j
  
# Sound only
model_s <- function (x,y) {
  1/(1 + (1-bA)*exp((-4/vrA)*x+(8/vrA)))
}

# Visual only
model_c <- function (x,y) {
  1/(1 + (1-bV)*exp((-4/vrV)*y+(8/vrV)))
}

# Optimal
model_opt <- function (x,y) {
  
  1/(1 + (1-bj)*exp((-4/vrA)*x+(-4/vrV)*y+(8/vrA)+(8/vrV)))
}


# Descriptive
model_des <- function (x,y) {
  1/(1 + (1-bj)*exp((-4/vrAj)*x+(-4/vrVj)*y+(8/vrAj)+(8/vrVj)))
}

exp4_s <- exp4_good %>% filter(condition =='sound')
exp4_c <- exp4_good %>% filter(condition =='concept')
exp4_j <- exp4_good %>% filter(condition =='joint')


#next used this new dataset to run the rest of the code

simu_s <- data.frame()
simu_c <- data.frame()
simu_j <- data.frame()
#x <- c("ID", "bimod")
#colnames(simlations) <- x

#

for (i in 1:50) {

simu_temp_s <- exp4_s %>%
  mutate(ID_2 = paste(ID,'_',i, sep="")) %>%
  mutate(prob = model_s(sound_dist, concept_dist)) %>%
  rowwise() %>%
  mutate(answer_simu = rbinom(1, 1, prob=prob)) %>%
  select(-ID) %>%
  rename(ID=ID_2)
  
simu_temp_c <- exp4_c %>%
  mutate(ID_2 = paste(ID,'_',i, sep="")) %>%
  mutate(prob = model_c(sound_dist, concept_dist)) %>%
  rowwise() %>%
  mutate(answer_simu = rbinom(1, 1, prob=prob)) %>%
  select(-ID) %>%
  rename(ID=ID_2)

simu_temp_j <- exp4_j %>%
  mutate(ID_2 = paste(ID,'_',i, sep="")) %>%
  mutate(prob = model_des(sound_dist, concept_dist)) %>%
  rowwise() %>%
  mutate(answer_simu = rbinom(1, 1, prob=prob)) %>%
  select(-ID) %>%
  rename(ID=ID_2)

simu_s <- bind_rows(simu_s, simu_temp_s)
simu_c <- bind_rows(simu_c, simu_temp_c)
simu_j <- bind_rows(simu_j, simu_temp_j)
  
}
  

```

```{r}
#Here anlysese of individual models

#Models 

#Sound Unimodal
fit_s <- function(data) {
  nls(answer ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), 
                 data=data,
                 start = list(e=0, vrA=1),
                 nls.control(warnOnly = TRUE)) 
}

fit_simu_s <- function(data) {
  nls(answer_simu ~ 1/(1+(1-e)*exp((-4/vrA)*sound_dist+(8/vrA))), 
                 data=data,
                 start = list(e=0, vrA=1),
                 nls.control(warnOnly = TRUE)) 
}
#Concept Unimodal
fit_c <- function(data, response) {
  nls(answer ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), 
                 data=data,
                 start = list(e=0, vrV=1),
                 nls.control(warnOnly = TRUE)) 
}

fit_simu_c <- function(data, response) {
  nls(answer_simu ~ 1/(1+(1-e)*exp((-4/vrV)*concept_dist+(8/vrV))), 
                 data=data,
                 start = list(e=0, vrV=1),
                 nls.control(warnOnly = TRUE)) 
}


#Joint sound-concept
fit_j <- function(data, response) {
  nls(answer ~1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), 
                 data=data,
                 start = list(e=0, vrA_j=1, vrV_j=1),
                 nls.control(warnOnly = TRUE)) 
}

fit_simu_j <- function(data, response) {
  nls(answer_simu ~1/(1+(1-e)*exp((-4/vrA_j)*sound_dist+(-4/vrV_j)*concept_dist+(8/vrA_j)+(8/vrV_j))), 
                 data=data,
                 start = list(e=0, vrA_j=1, vrV_j=1),
                 nls.control(warnOnly = TRUE)) 
}

##Fit the models for each subject

#Split data by subject real
data_by_subj_s <- split(exp4_s, exp4_s$ID) 
data_by_subj_c <- split(exp4_c, exp4_c$ID)
data_by_subj_j <- split(exp4_j, exp4_j$ID)

# fit the empirical data
model_by_subj_s <- map(data_by_subj_s, fit_s) 
model_by_subj_c <- map(data_by_subj_c, fit_c)
model_by_subj_j <- map(data_by_subj_j, fit_j)

#Split data by subject simulated
data_by_subj_s <- split(simu_s, simu_s$ID) 
data_by_subj_c <- split(simu_c, simu_c$ID)
data_by_subj_j <- split(simu_j, simu_j$ID)

#.. and the simulated data
model_by_subj_simu_s <- map(data_by_subj_s, fit_simu_s) 
model_by_subj_simu_c <- map(data_by_subj_c, fit_simu_c)
model_by_subj_simu_j <- map(data_by_subj_j, fit_simu_j)

## Convergence info


```


```{r}

##Extract coefficients 

#Unimodal coefficients
 co_uni <- function(model, ID) {
   data.frame(bias=coefficients(model)[1], 
              variance=coefficients(model)[2], 
              convergence=model$convInfo$stopMessage,
              ID=ID)
 }
 
 #Bimodal coefficients
 co_bim <- function(model, ID) {
   data.frame(bias=coefficients(model)[1],
              var_s=coefficients(model)[2],
              var_c=coefficients(model)[3],
              convergence=model$convInfo$stopMessage,
              ID=ID)
 }

ID_real <- as.list(strsplit(names(model_by_subj_s), " "))
ID_simu <- as.list(strsplit(names(model_by_subj_simu_s), " "))

#Here extract ceofficients to build optimal model later
coef_s <- map2(model_by_subj_s, ID_real, co_uni) %>%
  bind_rows() %>%
  rename(vrA_u= variance,
         bA_u =  bias,
         conv_A = convergence)

coef_simu_s <- map2(model_by_subj_simu_s, ID_simu, co_uni) %>%
  bind_rows() %>%
  rename(vrA_u= variance,
         bA_u =  bias,
         conv_A = convergence)


coef_c <- map2(model_by_subj_c, ID_real, co_uni) %>%
  bind_rows() %>%
  rename(vrV_u= variance,
         bV_u =  bias,
         conv_V = convergence)

coef_simu_c <- map2(model_by_subj_simu_c, ID_simu, co_uni) %>%
  bind_rows() %>%
  rename(vrV_u= variance,
         bV_u =  bias,
         conv_V = convergence)

coef_j <- map2(model_by_subj_j, ID_real, co_bim) %>%
  bind_rows() %>%
  rename(vrA_j = var_s,
         vrV_j = var_c,  
         b =  bias,
         conv_j = convergence)

coef_simu_j <- map2(model_by_subj_simu_j, ID_simu, co_bim) %>%
  bind_rows() %>%
  rename(vrA_j = var_s,
         vrV_j = var_c,  
         b =  bias,
         conv_j = convergence)

```

```{r}
## Below are functions that take sound and concept distances and return the predicted joint value in each model

# Sound only
model_s <- function (data, x,y) {
  vrA = unique(data$vrA_u)
  b = unique(data$bA_u)
  
  1/(1 + (1-b)*exp((-4/vrA)*x+(8/vrA)))
}

# Visual only
model_c <- function (data, x,y) {
  vrV = unique(data$vrV_u)
  b = unique(data$bV_u)
  
  1/(1 + (1-b)*exp((-4/vrV)*y+(8/vrV)))
}

# Optimal
model_opt <- function (data, x,y) {
  vrA = unique(data$vrA_u)
  vrV = unique(data$vrV_u)
  e   = unique(data$b)
  
  1/(1 + (1-e)*exp((-4/vrA)*x+(-4/vrV)*y+(8/vrA)+(8/vrV)))
}

# Descriptive
model_des <- function (data, x,y) {
  vrA = unique(data$vrA_j)
  vrV = unique(data$vrV_j)
  e   = unique(data$b)
  
  1/(1 + (1-e)*exp((-4/vrA)*x+(-4/vrV)*y+(8/vrA)+(8/vrV)))
}


data_models <- exp_good %>%
  filter(condition == "joint",
         experiment == "Experiment4") %>%
  group_by(ID, concept_dist, sound_dist) %>%
  summarise(mean = mean(answer)) %>%
  ungroup() %>%
  left_join(coef_s) %>%
  left_join(coef_c) %>%
  left_join(coef_j)

data_models_simu <- simu_j %>%
  group_by(ID, concept_dist, sound_dist) %>%
  summarise(mean = mean(answer)) %>%
  ungroup() %>%
  left_join(coef_simu_s) %>%
  left_join(coef_simu_c) %>%
  left_join(coef_simu_j)

data_models_good <- data_models %>%
  filter(conv_A == "converged",
         conv_V == "converged",
         conv_j == "converged")

data_models_good_simu <- data_models_simu %>%
  filter(conv_A == "converged",
         conv_V == "converged",
         conv_j == "converged")

N_conv <- data_models_good %>% 
  distinct(ID) %>%
  nrow()

N_conv_simu <- data_models_good_simu %>% 
  distinct(ID) %>%
  nrow()
```
  
```{r}
models <- function (subject_data) {
  subject_data %>% rename(Joint = mean) %>%
  mutate(Descriptive = model_des(subject_data, sound_dist, concept_dist)) %>%
  mutate(Optimal = model_opt(subject_data, sound_dist, concept_dist)) %>%
  mutate(Auditory = model_s(subject_data, sound_dist, concept_dist)) %>%
  mutate(Visual = model_c(subject_data, sound_dist, concept_dist)) %>%
  gather(model, pred, Visual, Auditory, Optimal, Descriptive) 
}

data_by_subj <- split(data_models_good, data_models_good$ID) 

data_preds <- map(data_by_subj, models) %>%
  bind_rows()

data_preds$model <- factor(data_preds$model, levels = c('Visual','Auditory', 'Optimal', 'Descriptive'))

correlations <- data_preds %>%
  group_by(ID, model) %>%
  summarise(cor = round(cor(Joint, pred)^2, 2))

```
Individual distribution

```{r}
weight <- data_models_good %>%
  group_by(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
  select(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
  unique() %>%
  mutate(weight_u = vrA_u/vrV_u,
         weight_b = vrA_j/vrV_j) %>%
  mutate(prop = weight_u/weight_b) %>%
  mutate(type='real')

weight_simu <- data_models_good_simu %>%
  group_by(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
  select(ID, vrA_u, vrV_u, vrA_j, vrV_j) %>%
  unique() %>%
  mutate(weight_u = vrA_u/vrV_u,
         weight_b = vrA_j/vrV_j) %>%
  mutate(prop = weight_u/weight_b) %>%
  mutate(type='simulated')

weight_both <- weight %>%
  bind_rows(weight_simu)


feather::write_feather(weight_both, "ind_weights.feather")
#weight <- feather::read_feather("ind_weights.feather")


weight_simu_low <- quantile(weight_simu$prop, 0.05)
weight_simu_up <- quantile(weight_simu$prop, 0.95) 

#Number of subject relying on the visual modality (p < 0.05) and the auditory modality (p > 0.95)

subj_all <- weight %>%
  nrow()

subj_vis <- weight %>%
  filter(prop < weight_simu_low) %>%
  nrow()

subj_aud <- weight %>%
  filter(prop > weight_simu_up) %>%
  nrow()
  
  
ggplot(data=weight_both, aes(x=prop, y=..ncount..)) +
  geom_histogram(data=subset(weight_both, type=='real'), fill="red", alpha=0.2, binwidth = 0.4)+
  geom_histogram(data=subset(weight_both, type=='simulated'), fill="blue", alpha=0.1, binwidth = 0.4)+
  #geom_histogram(data=subset(bimod_all, data=='simulation'), fill="blue", alpha=0.2, binwidth = 0.2)+
  #geom_histogram(binwidth = 0.2) +
  geom_vline(xintercept = weight_simu_low, linetype='dashed') +
  geom_vline(xintercept = weight_simu_high, linetype='dashed')+
 scale_x_log10(breaks =c(0.1,1,10)) +
   xlab("Optimal weighing relative to real weighing") +ylab("Count")+
  theme_few()+
  theme(aspect.ratio = 0.7) #+
  #coord_cartesian(xlim=c(0.01,100))



```

```{r}

#What does the mean data say 
#generate two data point from a binomial with probabilty model_fit1()
#loop over visual and auditory distance/ or create  adataframe with 

#For each subject, simulate the auditory, and visual responses as well as bimodal (descriptive) mod

 

```

